---
title: "TikTok in R Files: An example of the tiktokrmd package"
author: "Laura Ellis"
date: "1/16/2021"
output: html_document
---

# TikTok in R?!?!

Late last week, [Garrick Aden-Buie](https://twitter.com/grrrck) [announced a new package](https://twitter.com/grrrck/status/1349729420508946435) that allow us to embed TikTok videos into R Markdown files.  The package is called `tiktokrmd` and can be found [here](https://github.com/gadenbuie/tiktokrmd). It should also be noted that Garrick, has a number of other fun samples and packages on [his website](https://www.garrickadenbuie.com/project/), that I highly encourage y'all to check out. 


## Install the Package

Installing the package is straight forward through the `install_github()` function in the `remotes` package.  This happened to be the first new package I downloaded from GitHub on a repo that was created since the default branch was named `main`, so I encountered the need to employ one of two techniques below.

1) You can just update the remotes package as [Garrick](https://twitter.com/grrrck) [pointed out](https://twitter.com/grrrck/status/1350504524901920773?s=20).

2) You can specify the branch as @main as I [pointed out in a tweet.](https://twitter.com/LittleMissData/status/1350473247788310536)


```{r }

#1) Update remotes to find the default branch
#install.packages("remotes")
#library(remotes)
#remotes::install_github("gadenbuie/tiktokrmd")

#2) Or if you have the remotes package installed and don't want to or can't re-install, you can just specify the branch
remotes::install_github("gadenbuie/tiktokrmd@main")
library(tiktokrmd)
```


## Embed your favorite TikTok video

This is probably the easiest tutorial I've written, just because of how simple Garrick has made his package.  As per the instructions on his GitHub repo, simply set a variable to the TikTok video URL, pass it through the `tiktok_embed` function, and then pass that through the `tiktok_html` function.

For my example, I am including my favorite data TikTok by [Chelsea Parlett](https://www.tiktok.com/@chelseaparlettpelleriti?lang=en).  I highly encourage y'all to check out her videos!

```{r}
tt_url <- "https://www.tiktok.com/@chelseaparlettpelleriti/video/6811647290709757189"
tt <- tiktok_embed(tt_url)
```


#### Display 

```{r}
tt

```

#### Display with plain markdown

```{r}

tiktok_md(tt)

```


#### Display in html with player

```{r}
tiktok_html(tt, include_player = FALSE)

```


## Knit to HTML and host online

In the repo, Garrick [points out](https://github.com/gadenbuie/tiktokrmd#%EF%B8%8F-previewing-locally-%EF%B8%8F) that the html file needs to be hosted somewhere to fully display the video.  Luckily GitHub pages has us covered.  [Just follow the steps in my previous blog here](https://www.littlemissdata.com/blog/pretty-r-tables-in-github) to host your html, .Rmd output on GitHub pages. 


## Thank You

Thank you for following along and good luck with trying out the package!

